Dynamical properties of the Benguela Current as seen through a cold-spell algorithm.

### 2019-02-23 Write_up/Writing/Chapter1_Intro.Rmd
upadted

---
title: "Introduction_outline"
author: "Amieroh Abrahams"
date: "13 January 2019"
output:
  pdf_document: default
  html_document: default
fontsize: 10pt
geometry: margin=1in
language: Australian
mainfont: Minion Pro
monofont: Courier
papersize: A4
sansfont: Myriad Pro
tables: yes
bibliography: ../bib_master.bib
---

>>>>

---
title: "Dynamical properties of the Benguela Current as seen through a cold-spell algorithm."
author: "Amieroh Abrahams"
date: "13 January 2019"
output:
  pdf_document: default
  html_document: default
fontsize: 10pt
geometry: margin=1in
language: Australian
mainfont: Minion Pro
monofont: Courier
papersize: A4
sansfont: Myriad Pro
tables: yes
bibliography: ../bib_master.bib
---
